
## OHDSI-UK

### Background 

The United Kingdom has more than 20 Data Partners in the EHDEN network and several EHDEN-certified SMEs. The UK scientific network is dynamic and research active, with numerous initiatives in the fields of health informatics, health data sciences, pharmacoepidemiology, and related areas.

Many UK partners have made substantial contributions to recent EHDEN- and OHDSI-sponsored research, and key national players like Health Data Research UK and the National Institute for Health and Care Excellence (NICE) are increasingly interested in the use of OMOP for federated analytics nationally.

### Objectives 

The aims of the UK national node include:

- To adopt OHDSI’s mission, vision, and values
- To facilitate the coordination of national members at a national and international level with OHDSI and EHDEN partners
- To promote the OHDSI mission in the UK in collaboration with relevant national stakeholders including academia, healthcare organizations, HTA agencies, regulators, patient organizations, policy makers, clinical guideline developers and pharmaceutical and life science industry
- To initiate and/or collaborate in relevant national research collaborations and co-ordination with European and global OHDSI initiatives
- To organize training programs in the field of Health Data Sciences and related areas
- To engage with the European and global OHDSI leadership

### Leading Organisation 

Health Data Sciences Section, Botnar Research Centre, University of Oxford

### Collaborators

```{r, echo=FALSE, message=FALSE}
x <- "https://docs.google.com/spreadsheets/d/1ojn50In5Knkcak5Dw-OO8dwzGQqHziBXkCLV-Q-US14/export?format=csv" |>
  readr::read_csv(col_types = c(longitude = "c", latitude = "c")) |>
  dplyr::select("data_partner_name", "longitude", "latitude") |>
  dplyr::mutate(dplyr::across(c("longitude", "latitude"), \(x) as.numeric(gsub(",", ".", x))))
```

The node currently has `r nrow(x)` collaborators, you can find more information about each one of them in [Collaborators](collaborators.qmd). See them located in this map:

```{r, echo=FALSE}
x |>
  dplyr::filter(!is.na(.data$latitude) & !is.na(.data$longitude)) |>
  leaflet::leaflet() |>
  leaflet::addTiles() |>
  leaflet::setView(lng = -3, lat = 54.5, zoom = 5) |>
  leaflet::addMarkers(lng = ~longitude, lat = ~latitude, popup = ~data_partner_name)
```

### How to contribute?

Any UK-based institution interested to join the UK OHDSI Node should get in touch with the coordinator: [prietoalhambra@ohdsi.org](mailto:prietoalhambra@ohdsi.org)
